%\iffalse
%
%INSTRUCTIONS: (if this is not lecture1.tex, use the right file name)
%
%  Clip out the ********* INSERT HERE ********* bits below and insert
%appropriate TeX code.  Once you are done with your file, run
%
%  ``latex lecture1.tex''
%
%from a UNIX prompt.  If your LaTeX code is clean, the latex will exit
%back to a prompt.  Once this is done, run
%
%  ``dvips lecture1.dvi''
%
%which should print your file to the nearest printer.  There will be
%residual files called lecture1.log, lecture1.aux, and lecture1.dvi.
%All these can be deleted, but do not delete lecture1.tex.
%\fi
%%
\documentclass[11pt]{article}
\usepackage{amsfonts}
\usepackage{latexsym}
\setlength{\oddsidemargin}{.25in}
\setlength{\evensidemargin}{.25in}
\setlength{\textwidth}{6in}
\setlength{\topmargin}{-0.4in}
\setlength{\textheight}{8.5in}

\newcommand{\handout}[5]{
   \renewcommand{\thepage}{#1-\arabic{page}}
   \noindent
   \begin{center}
   \framebox{
      \vbox{
    \hbox to 5.78in { {\bf CSC 591 Cryptography} \hfill #2 }
       \vspace{4mm}
       \hbox to 5.78in { {\Large \hfill #5  \hfill} }
       \vspace{2mm}
       \hbox to 5.78in { {\it #3 \hfill #4} }
      }
   }
   \end{center}
   \vspace*{4mm}
}

\newcommand{\lecture}[3]{\handout{L#1}{#2}{Lecturer: Alessandra Scafuro}{Scribe: #3}{Lecture #1}}

\def\squarebox#1{\hbox to #1{\hfill\vbox to #1{\vfill}}}
\def\qed{\hspace*{\fill}
        \vbox{\hrule\hbox{\vrule\squarebox{.667em}\vrule}\hrule}}
\newenvironment{solution}{\begin{trivlist}\item[]{\bf Solution:}}
                      {\qed \end{trivlist}}
\newenvironment{solsketch}{\begin{trivlist}\item[]{\bf Solution Sketch:}}
                      {\qed \end{trivlist}}
\newenvironment{proof}{\begin{trivlist}\item[]{\bf Proof:}}
                      {\qed \end{trivlist}}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{observation}[theorem]{Observation}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{fact}[theorem]{Fact}
\newtheorem{assumption}[theorem]{Assumption}

%Put more macros here, as needed.
\newcommand{\al}{\alpha}
\newcommand{\Z}{\mathbb Z}

\begin{document}

\lecture{CPA-Secure Encryption Scheme}{9/26/18}{Bihan Zhang}

\section*{Topic/Problem}
This is the second lecture on CPA, with a focus on constructing a CPA-secure encryption scheme with a PRF.

\subsection*{Definition}

An encryption scheme is \textit{CPA} secure if it is secure against chosen plaintext attacks.


The CPA game ($Priv^{CPA}_{A,\Pi}(n)$) is as follows:

\hspace{\parindent} 1. Let $\Pi$ be an encryption oracle.

\hspace{\parindent}	2. Let $A_{PPT}$ be an adversary

\hspace{\parindent}	3. Training Phase: $A_{PPT}$ can pass multiple messages $m_i$ to $\Pi$ and get the encrypted ciphertext $c_i$ back.

\hspace{\parindent}	4. Challenge Phase: 

\hspace{\parindent}\hspace{\parindent} a. $A_{PPT}$ passes $\{m_0, m_1\}$ to $\Pi$. 

\hspace{\parindent}\hspace{\parindent} b. $\Pi$ picks a random bit $b\gets_R \{0,1\}$ and returns $c_b= Enc(m_b)$ 

\hspace{\parindent}\hspace{\parindent} c. $A_{PPT}$ guesses $b'$ ($b'$ is whichever $m_0$, or $m_1$ $A_{PPT}$ thinks $\Pi$ encrypted.

\hspace{\parindent}\hspace{\parindent} d. $A_{PPT}$ wins if $b==b'$


For a CPA secure encryption scheme:

$$Pr[A \textrm{ wins } Priv_\Pi^{CPA}] = 1/2 + \epsilon_1$$
$$Pr[A \textrm{ wins } Priv_{TR}^{CPA}] = 1/2 + \epsilon_2$$
$$Pr[A \textrm{ wins } Priv_{TR}^{CPA}] - Pr[A \textrm{ wins } Priv_\Pi^{CPA}] \leq |\epsilon_1 - \epsilon_2|$$

Where $\epsilon_1, \epsilon_2$ are both negligible functions.


-----------------------------------------

A function $F: \{0,1\}^* \times \{0,1\}^* \rightarrow \{0,1\}^*$ is considered pseudorandom if for all distinguishers $D_{PPT}$ the following holds true:\\

$$|Pr[D^{F_k}\rightarrow 1] - Pr[D^{TR}\rightarrow1]| \leq \epsilon$$

Where $TR$ is truly random, and $\epsilon$ is a negligible function.\\

Or, in layman's terms, there does not exist a distinguisher that can tell apart the output of a PRF, and the output of a truly random function. The distinguisher can play the PRF Game in order to prove that it can tell the the two apart.


The PRF Game:\\

\hspace{\parindent} 1. Let $O$ be an oracle instantiated with either $F_k$ or with $TR$.

\hspace{\parindent} 2. Let $D_{PPT}$ be a distinguisher with access to $O$.

\hspace{\parindent} 3. $D_{PPT}$ passes $x_i$ to $O$

\hspace{\parindent} 4. $O$ will either return $y_i = PRF(x_i)$ or $y_i = TR()$

\hspace{\parindent} 5. $D_{PPT}$ guesses whether $y_i$ came from the PRF or from TR.


$$D_{PPT} \textrm{ wins if }|Pr[D^{F_k}\rightarrow 1] - Pr[D^{\{0,1\}^n}=1]| = p(n)$$
Where $p(n)$ is a non-negligible function.


\subsection*{Scheme}
CPA secure encryption: 
Let $F$ be a pseudorandom function. Let $\Pi$ be (Gen, Enc, Dec) as described:\\

\hspace{\parindent} Gen: $k \in \{0,1\}^n$\\

\hspace{\parindent} Enc(k, m): Given $k \epsilon \{0,1\}^n$ and $m \epsilon \{0,1\}^n$ choose a uniformly random $r \epsilon \{0,1\}^n$ and construct $c = <F_k(r)\oplus m, r>$\\

\hspace{\parindent} Dec(k,c): Given $k \epsilon \{0,1\}^n$ and $c=<s,r>$ construct $m= F_k(r)\oplus s$


\subsection*{Security Proof}

If $F$ is a PRF, $\Pi$ is secure.\\

\textbf{Intuition:}

Even though intuitively it feels insecure to reveal $r$ it actually doesn't matter. Even when $r$ is known, since $k$ is unknown, the result of $F_k(r)$ is indistinguishable from a random function. And because the output of $F_k(r)$ is pseudo-random, $F_k(r) \oplus m $ should be secure, and because $r$ is a random value each time, the scheme is non-deterministic, and should be CPA secure. \\


\textbf{Formal Proof:}

Assume for the sake of contradiction that there exists an Adversary $A_{CPA}$ that can win the $\Pi$ CPA game with some non negligible probability $p(n)$.\\


$$Pr[A \textrm{ wins } Priv_\Pi^{CPA}] = 1/2 + p(n)$$
$$Pr[A \textrm{ wins } Priv_{TR}^{CPA}] = 1/2 + q/2^n$$

$q$ is the number of queries performed by the adversary. There is a chance that the adversary has seen the random string $r$ repeating, and this chance increases with the number of queries. This is very unlikely, so we'll treat $q/2^n = \epsilon$, where $\epsilon$ is a negligible function.


$$|Pr[A \textrm{ wins } Priv_{TR}^{CPA}]-Pr[A \textrm{ wins } Priv_\Pi^{CPA}] | = p(n)$$

\textbf{Reduction}
A distinguisher $D$ for $F$ can be constructed as follows:

	\hspace{\parindent}Assume $D$ has oracle access to a function $O$. $O$ is either instantiated with $F$, or with a truly random function $TF$.
	
	\hspace{\parindent}Assume also that $D$ can run adversary $A_{CPA}$
	
	\hspace{\parindent}When $A_{CPA}$ is in it's training phase, it'll ask for encryptions of messages $m_i$, when this happens $D$ does the following:
	
	\hspace{\parindent} 1. Pick a random $r_i = \{0,1\}^n$
	
	\hspace{\parindent} 2. Query the Oracle $O$ with $r_i$ and receive $y_i$
		
	\hspace{\parindent} 3. Output $<r_i, m_i \oplus y_i>$\\

	\hspace{\parindent} When $A_{CPA}$ challenges with $m_0, m_1$, $D$ does the following:
	
	\hspace{\parindent} 1. Pick $b\gets_R \{0,1\}$ 
	
	\hspace{\parindent} 2. Pick a random $r_i = {0,1}^n$
	
	\hspace{\parindent} 3. Query the Oracle $O$ with $r_i$ and receive $y_i$
	
	\hspace{\parindent} 4.  Output $\langle r_i, m_b \oplus y_i \rangle$\\
	
	\hspace{\parindent} When $A_{CPA}$ enters its decision phase and outputs a bit $b'$. D should return 1 if $b==b'$, and 0 otherwise


\textbf{Analysis:}

If $O$ is instantiated with $F$ then the reduction is perfectly simulating the game $Priv^{CPA}_\Pi$ and therefore:

$$Pr[D^F \rightarrow 1] = Pr[A \textrm{ wins } Priv^{CPA}_\Pi] = 1/2 + p(n)$$

Where $p(n)$ is non-negligible.


If $O$ is instantiated with $TR$ then $D$ is simulating $Priv^{CPA}_{TR}$ and so:

$$Pr[D^{TR} \rightarrow 1] = Pr[A \textrm{ wins } Priv^{CPA}_{TR}] = 1/2 + \epsilon$$

Where $\epsilon$ is negligible

$$|Pr[D^F \rightarrow 1]-Pr[D^{TR} \rightarrow 1]| = p(n) - \epsilon$$

This contradicts with our original assumption that F is a PRF and:

$$|Pr[D^{F_k}\rightarrow 1] - Pr[D^{\{0,1\}^n}\rightarrow1]| \leq \epsilon$$


Therefore if $F$ is a PRF, $\Pi$ is a CPA secure scheme.

\end{document}

